For Induction-Induction, Induction is Enough

### 2019-11-12 paper/paper.tex
grammar and typos
Brunerie et al

Voevodsky was interested in constructing initial models of type
theories from presyntaxes. Inspired by this, Brunerie \cite{brunerie}
formalised Streicher's proof in Agda for a type theory with $\Pi$,
$\Sigma$, $\mathbb{N}$, identity types and an infinite hierarchy of
universes. He used UIP, function extensionality and quotient types in
his formalisation. In this paper we construct a type theory without
computation rules, hence we avoid using quotients.

@@

We construct all IITs describable by the theory of IIT signatures through the
term model construction of \cite{Kaposi:2019:CQI:3302515.3290315}. There, it is
shown that from the syntax of the theory of signatures for finitary QIITs, one
can construct any particular finitary QIIT. The idea is that for a signature
$\Gamma$, the initial algebra can be built from sets of terms of the form
$\Tm\,\Gamma\,(\El\,a)$. For example, considering the signature for natural
numbers
\[
  \Gamma := \big(\boldsymbol{\cdot}\,\ext\,N:\U\,\ext\,z : \El\,N\,\ext\,s : N \ra \El\,N\big),
\]
we have that $\Tm\,\Gamma\,(\El\,N)$ is the set of natural numbers up to isomorphism,
since the only way to construct these terms is by using $s$ and $z$ from $\Gamma$.

>>>>

Voevodsky was interested in constructing initial models of type
theories from presyntaxes. Inspired by this, Brunerie et al.\ \cite{brunerie}
formalised Streicher's proof in Agda for a type theory with $\Pi$,
$\Sigma$, $\mathbb{N}$, identity types and an infinite hierarchy of
universes. He used UIP, function extensionality and quotient types in
his formalisation. In this paper we construct a type theory without
computation rules, hence we avoid using quotients.

@@

We construct all IITs describable by the theory of IIT signatures through the
term model construction of \cite{Kaposi:2019:CQI:3302515.3290315}. There, it is
shown that from the syntax of the theory of signatures for finitary QIITs, one
can construct any particular finitary QIIT. The idea is that for a signature
$\Gamma$, the initial algebra can be built from sets of terms of the form
$\Tm\,\Gamma\,(\El\,a)$. For example, considering the signature for natural
numbers
\[
  \Gamma := \big(\boldsymbol{\cdot}\,\ext\,N:\U\,\ext\,z : \El\,N\,\ext\,s : N \Ra \El\,N\big),
\]
we have that $\Tm\,\Gamma\,(\El\,N)$ is the set of natural numbers up to isomorphism,
since the only way to construct these terms is by using $s$ and $z$ from $\Gamma$.
